The \dealii Library, Version 9.6

### 2024-09-22 9.6/paper.tex
Minor corrections for the description of the TpetraWrapper classes.

In the current release, we have put substantial work into this switch,
as outlined below. In the following list, we omit the common namespace
\texttt{LinearAlgebra::} prefix on all mentioned
\texttt{TpetraWrappers} symbols for readability:
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
Most of the interfaces are usable at this point even if some functionality existing in the \texttt{TrilinosWrappers} classes
is still missing, most noticably a wrapper for an algebraic-multigrid preconditioner.

All the \texttt{TpetraWrappers} classes take \texttt{Number} and \texttt{MemorySpace} template arguments
allowing to control the underlying number type and the memory space used for storing the data. Note that the memory space type
also determines whether \tpetra{} takes advantage of GPUs if \texttt{Kokkos} has been configure with a GPU backend.

@@

Sebastian Kinnewig is supported by the Deutsche Forschungsgemeinschaft (DFG) under Germany’s Excellence
Strategy within the Cluster of Excellence PhoenixD (EXC 2122, Project ID 390833453)

>>>>

In the current release, we have put substantial work into this switch,
as outlined below. In the following list, we omit the common namespace
\texttt{LinearAlgebra::} prefix on all mentioned
\texttt{TpetraWrappers} symbols for readability:
\begin{itemize}
  \item The \texttt{TpetraWrappers::Vector} class has been overhauled to also allow specifying
    a memory space, and the \texttt{TpetraWrappers::BlockVector} class has been added.
  \item \texttt{TpetraWrappers::SparseMatrix} and \texttt{TpetraWrappers::SparsityPattern} have been implemented mirroring
    the functionality of the \texttt{TrilinosWrappers::SparseMatrix} \\ and \texttt{TrilinosWrappers::SparsityPattern} classes.
  \item Various \texttt{TpetraWrappers::Precondition*} classes have been added largely
    mirroring the exising preconditioners in the \texttt{LinearAlgbera::TrilinosWrappers} namespace.
  \item \texttt{TpetraWrappers::SolverDirect} and \texttt{TpetraWrappers::SolverDirectKLU2}
    have been implemented as direct solvers.
\end{itemize}
The preconditioner available in the \texttt{TpetraWrappers::Precondition*} classes can be used along with the existing 
iterative solvers, e.g., CG, GMRES, etc.; therefore, the interface is already usable. 
Even if some functionality exists, the \texttt{TrilinosWrappers} classes are missing, most noticably a wrapper for an 
algebraic-multigrid preconditioner.

The design goal was to introduce as few changes as possible for the user to allow for an easy transition to the 
\texttt{TpetraWrappers} classes. 
However, based on the difference between \epetra{} and \tpetra{}, the following changes were necessary:
\begin{itemize}
  \item The constructor for the class \texttt{TrilinosWrappers::MPI::Vector} only required the \texttt{IndexSet locally\_owned}, 
    which describes the set of indices locally owned by the current rank. 
    However, if one wants to create a vector that has read or write access to non-locally owned indices,  the constructor of the 
    \texttt{TpetraWrappers::Vector} requires \texttt{IndexSet locally\_owned}, the \texttt{IndexSet locally\_relevat}, and 
    a boolean flag, whether to initialize the vector in the read-only or the write-only state.
  \item A vector created without providing a \texttt{IndexSet locally\_relevat} is purely local and cannot access non-local indices. 
    Such a vector can not be copied to a vector that can access non-local indices, as the \texttt{IndexSet locally\_relevat} must 
    be provided at creating the vector object.
\end{itemize}

One other important change is that
all the \texttt{TpetraWrappers} classes take \texttt{Number} and \texttt{MemorySpace} template arguments,
which control the underlying number type and memory space. 
By default, the memory is allocated on the CPU, mirroring the behavior of the \texttt{TrilinosWrappers}. 
The support for different number types also enables the usage of automatic differentiation-based tools in 
\trilinos{}, such as \texttt{NOX}. 
Additionally, the memory space type determines whether \tpetra{} can utilize GPUs if \kokkos{} is configured 
with a GPU backend. 
To make the automatic differentiation tools of \trilinos{} accessible through the \tpetra{} interface without 
requiring users to have an in-depth understanding of \trilinos{}, additional wrappers for the corresponding 
\trilinos{} packages will be added in future releases. 
Furthermore, to fully leverage the GPU backend and unlock its full potential for users will require further work.

@@

\todo[inline]{Sebastian: Anything to list here?}
